### 2016-09-28 results.tex
rewriting GBF

%%%%%%%%%%%%%%%%% GARBLED BF  %%%%%%%%%%%%%%%%%%%%
\subsection{Garbled Bloom Filter}
\begin{figure}
\centering
\fpage{.525}
{
\algorithmv{$\Rep(S)$}\\
$M \gets (\bot)^m$\\
$K_1,K_2,\ldots, K_k \getsr \calK$\\
for $x \in S$\\
\nudge $\finalshare \gets 0^\lambda$; $\emptyslot \gets -1$\\
\nudge for $j \in \{1,2,\ldots, k\}$\\
\nudge \nudge $h_j \gets H_{K_j}(x)$\\
\nudge \nudge if $M[h_j] \neq \bot$ then\\
\nudge \nudge \nudge $\finalshare \gets \finalshare \xor M[h_j]$\\
\nudge \nudge else if $\emptyslot = -1$ then\\
\nudge \nudge \nudge $\emptyslot \gets h_j$\\
\nudge \nudge else\\
\nudge \nudge \nudge $M[h_j] \getsr \bits^\lambda$\\
\nudge \nudge \nudge $\finalshare \gets \finalshare \xor M[h_j]$\\
\nudge $M[\emptyslot] \gets \finalshare \xor x$\\
for $i \in \{1,2,\ldots, m\}$\\
\nudge if $M[i] = \undefined$ then\\
\nudge \nudge  $M[i] \getsr \bits^\lambda$\\
$\pubaux \gets M$; $\privaux \gets $???\\

\medskip
\algorithmv{$\Qry(\pubaux,\privaux,\qry_x)$}\\
$M \gets \pubaux$, ??? $\gets \privaux$\\
$x' \gets 0^\lambda$\\
for $j \in \{1,2,\dots,k\}$\\
\nudge $h_j \gets H_{K_j}(x)$\\
\nudge $x' \gets x' \xor M[h_j]$\\
if $x' =x $ then Return 1\\
Return 0
}
\caption{ $\Rep$ and $\Qry$ algorithms for garbled Bloom
  filter $\Pi_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \calK \times \mathbb{N} \times 
 \univ \to [m]$. The query set is $\calQ=\{\qry_x\colon
  \univ \to \bits\}$ where $\qry_x(S)=1 \Leftrightarrow x \in S$.}

@@

\begin{figure}
\centering
\hfpagess{.45}{.5}
{
\adversaryv{$A^{\TestOracle}(\pubaux)$}\\
$M \gets \pubaux$\\
for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if $\TestOracle(x)=1$ then Return $\bot$
}
{
\adversaryv{$A^{\TestOracle,H}(\pubaux)$}\\
$M \gets \pubaux$\\
for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge $x' \gets H(1,x) \xor H(2,x) \xor \cdots \xor H(k,x)$\\
\nudge if $x=x'$ then\\
\nudge\nudge $\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}

\caption{Adversary for Theorem~\ref{thm:xxx}.}
\label{fig:adv-bi-lin-ss}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%% GARBLED BF  %%%%%%%%%%%%%%%%%%%%
\subsection{Garbled Bloom Filter}
\begin{figure}
\centering
\fpage{.75}
{
\algorithmv{$\Rep(S)$}\\
$M \gets (\bot)^m$\\
$K_1,K_2,\ldots, K_k \getsr \calK$\\
for $x \in S$\\
\nudge $\finalshare \gets 0^\lambda$; $\emptyslot \gets -1$\\
\nudge for $j \in \{1,2,\ldots, k\}$\\
\nudge \nudge $h_j \gets H_{K_j}(x)$\\
\nudge \nudge if $M[h_j] \neq \bot$ then\\
\nudge \nudge \nudge $\finalshare \gets \finalshare \xor M[h_j]$\\
\nudge \nudge else if $\emptyslot = -1$ then\\
\nudge \nudge \nudge $\emptyslot \gets h_j$\\
\nudge \nudge else\\
\nudge \nudge \nudge $M[h_j] \getsr \bits^\lambda$\\
\nudge \nudge \nudge $\finalshare \gets \finalshare \xor M[h_j]$\\
\nudge $M[\emptyslot] \gets \finalshare \xor x$\\
for $i \in \{1,2,\ldots, m\}$\\
\nudge if $M[i] = \undefined$ then\\
\nudge \nudge  $M[i] \getsr \bits^\lambda$\\
$\pubaux \gets M$; $\privaux \gets \langle K_1,K_2,\ldots,K_k \rangle$ \mbox{ (if secret hash version)}\\
$\pubaux \gets \langle M,K_1,K_2,\ldots,K_k \rangle$; $\privaux \gets \emptystring$ \mbox{(if public hash version)}\\

\medskip
\algorithmv{$\Qry(\pubaux,\privaux,\qry_x)$}\\
if $\privaux \neq \emptystring$ then\\
\nudge $M \gets \pubaux$, $K_1,K_2,\ldots,K_k \gets \privaux$\\
else\\
\nudge $M,K_1,K_2,\ldots,K_k \gets \pubaux$\\
$x' \gets 0^\lambda$\\
for $j \in \{1,2,\dots,k\}$\\
\nudge $h_j \gets H_{K_j}(x)$\\
\nudge $x' \gets x' \xor M[h_j]$\\
if $x' =x $ then Return 1\\
Return 0
}
\caption{ $\Rep$ and $\Qry$ algorithms for garbled Bloom
  filter $\Pi_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \calK \times 
 \univ \to [m]$. The query set is $\calQ=\{\qry_x\colon
  \univ \to \bits\}$ where $\qry_x(S)=1 \Leftrightarrow x \in S$.}

@@

\begin{figure}
\centering
\hfpagess{.45}{.5}
{
\adversaryv{$A^{\TestOracle}(\pubaux)$}\\
$M \gets \pubaux$\\
for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge if $\TestOracle(x)=1$ then Return $\bot$
}
{
\adversaryv{$A^{\TestOracle}(\pubaux)$}\\
$M,K_1,K_2,\ldots,K_k \gets \pubaux$\\
for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
\nudge $x' \gets H(1,x) \xor H(2,x) \xor \cdots \xor H(k,x)$\\
\nudge if $x=x'$ then\\
\nudge\nudge $\TestOracle(x)$\\
\nudge\nudge Return $\bot$\\
}

\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} secret hash case, \textbf{Right:} public hash case.}
\label{fig:adv-bi-lin-ss}
\end{figure}
